\documentclass[../2.tex]{subfiles}
\begin{document}
In this section we will present some properties of the eigenfunctions of the classical laplacian operator.
So we momentarily leave the discrete setting and we recall some well known facts about the continuous one.
Let's first define the laplacian for smooth functions from $\R^n$ to $\R$. 

\begin{defn}
    Let $f : \R^n \to \R$ be a smooth function, then the laplacian of $f$ is a function $\Delta f : \R^n \to \R$ defined as
    \[ \Delta f(x) := - \sum_{i=1}^n \frac{\del f}{\del x_i}(x), \]
    where the $\frac{\del}{\del x_i}$ are the directional derivatives with respect to the basis of $\R^n$.
\end{defn}

The laplacian eigenfunctions, i.e. functions $f: \R^n \to \R$ such that $\Delta f = \lambda f$ with $\lambda \in \R$ , are the solution of a constrained variational problem for an action called \ii{Dirichlet energy}, as shown in \cite{bronstein}.

\begin{defn}
    Let $f:\R^n \to \R$ be a smooth funcion with compact support, we define the \ii{Dirichlet energy functional} to be
    \[ D[f] := \int_{\R^n} dx |\nabla f|^2 .\]
\end{defn}

\begin{prop}
    If $f:\R^n \to\R$ is a smooth function with compact support then 
    \[ D[f] := \int_{\R^n} dx |\nabla f|^2 = \int_{\R^n} dx f\Delta f .\]
    \label{prop:2:4:3}
\end{prop}
\begin{proof}
    Recall the definition of laplacian in $\R^n$ as $\Delta f := -\nabla \cdot \nabla f$, and we integrate by parts
    \[ 0 = \int_{\R^n} dx \nabla \cdot (f \nabla f) = \int_{\R^n} dx \nabla f \cdot \nabla f + \int_{\R^n} dx f \nabla \cdot \nabla f = \int_{\R^n} dx \nabla f \cdot \nabla f - \int_{\R^n} dx f \Delta f, \]
    hence the thesis. \qedhere
\end{proof}

The variational problem for the Dirichlet energy leads to the Euler-Lagrange equations when it is restricted to those functions which
vanish on the boundary of the domain of integration, which is true in the case of functions with compact support.
Further details and proofs of the following two propositions can be found in \cite{fomin} at chapters $35$ and $12$ respectively.

\begin{prop}
    Let $f:\R^n \to \R$ be a smooth function with compact support, and $\mc{L}(f,\nabla f) : \R^n \to \R$ a lagrangian,
    then the solutions of the variational problem 
    \[ \delta\int_{\R^n} dx \mc{L}(f,\nabla f) = 0 \]
    are the solutions of the Euler-Lagrange equations
    \[ \nabla \cdot \frac{\del \mc{L}}{\del(\nabla f)} - \frac{\del\mc{L}}{\del f} = 0. \]
\end{prop}

In order to solve the variational problem subject to constraints we need a variational 
version of the Lagrange multipliers theorem.

\begin{prop}
    Let $f:\R^n \to \R$ be a smooth function with compact support, and $\mc{L}(f,\nabla f) : \R^n \to \R$ a sufficiently regular lagrangian,
    then the solutions of the variational problem 
    \[ \delta\int_{\R^n} dx \mc{L}(f,\nabla f) = 0 \]
    with constraint
    \[ \int_{\R^n} dx f^2 = 1 \]
    are the solutions of the Euler-Lagrange equations for the lagrangian
    \[ \mc{L}(f,\nabla f) - \lambda f^2, \]
    where $\lambda$ is a Lagrange multiplier.
\end{prop}

We now apply this to the Dirichlet energy.

\begin{prop}
    The solution of the variational problem for the Dirichlet energy
    \[ \delta\int_{\R^n} dx | \nabla f |^2 = 0 \]
    constrained to the functions such that 
    \[ \int_{\R^n} dx f^2 = 1 \]
    are the eigenfunctions of the laplacian.
\end{prop}
\begin{proof}
    Namely for $\mc{L} = |\nabla f|^2-\lambda f^2$ the Euler-Lagrange equation reads as $ 2 \Delta f - 2\lambda f = 0$,
    hence \[ \Delta f = \lambda f . \qedhere \]

\end{proof}

Obviously, the eigenfunction that truly minimizes the Dirichlet energy is the one corresponding to the lowest eigenvalue,
since for the eigenfunctions $D[f] = \int_{\R^n} dx f \Delta f = \lambda \int_{\R^n} dx f^2 = \lambda$. We can also see how the Dirichlet energy
measures the smoothness of a function. As pointed out in \cite{2021geo} the deformation stability of the data is related to its Dirichlet energy.\\
\hfill \\

% Another interesting property of the laplacian eigenfunctions comes from quantum mechanical considerations.
% In fact, the laplacian, neglecting the constants, is the hamiltonian of the free particle in the Schr\"{o}dinger representation.

% \begin{prop}
%     The functions $e^{ip\cdot x} : \R^n \to \C$, where $p \in R^n$, are a generalized orthogonal basis of laplacian eigenfunctions.
% \end{prop}
% \begin{proof} 
%     First we see that $\Delta e^{ip\cdot x} = \nabla \cdot (ipe^{ip\cdot x}) = -p^2 e^{ip\cdot x}$.
%     Then, in a suitable space where the Fourier transform is invertible we have that $f(x') = \int_{\R^n} dp e^{i\scal{x'}{p}}\int_{\R^n} dx e^{-i\scal{x}{p}}f(x)$, 
%     \\where $\int_{\R^n} dp e^{i\scal{x'-x}{p}} = \delta(x-x')$ up to constants that can be reabsorbed in the eigenfunctions, hence the generalized completness relation (see App. \ref{app:B}). \qedhere
% \end{proof}

% In this approach the Fourier transorm is nothing more than a change of generalized basis into the basis of the eigenfunctions of the laplacian.

% Let's recall the definition of convolution in $\R^n$.

% \begin{defn}
%     Let $f,g : \R^n \to \C$ be sufficiently regular functions we define the \ii{convolution} of $f$ with $g$ as
%     \[ (f * g)(x) = \int_{\R^n} dx' f(x')g(x-x').\]
% \end{defn}

% The well known theorem that follows states that the Fourier transform, as a change of generalized basis, diagonalizes the convolution.

% \begin{thm}
%     Let $\mc{F}$ denote the fourier transform, then for sufficiently regular functions $f,g : \R^n \to \C$ we have that
%     \[ \mc{F}(f * g) = (\mc{F}f)(\mc{F}g).\]
% \end{thm}

% This approach will allow us in Chapter \ref{ch:3} to define a similar convolution as an operator which is diagonalized by the laplacian eigenfunctions.
    
\end{document}